### 2015-02-27 icfp15-servo/servo.tex

The Rust compiler has plugin framework that provides a couple of hooks that programmers can use to extend the behavior of the compiler. In particular, one can perform arbitrary expansion on the AST and define custom warnings or errors (which also operate on the AST).

We have used this to great effect to interface with the Spidermonkey garbage collector. We can enforce, at compile time, that all objects dealing with DOM structs have trace hooks, as well as limiting the amount of ways GC-managed structs can be used to avoid leaking them.

Future plans include hardening our GC safety checks and introducing compile time checks intended to improve performance, for example to reduce redundant cloning of data.

>>>>

The Rust compiler has a plugin framework that allows programmers to modify the behaviour of the compiler. In particular,
it is possible to define arbitrary AST transformations, as well as custom warnings or errors (which also operate on the AST).

These capabilities enable a safer and more correct interface to the SpiderMonkey garbage collector. For example, we
can enforce at compile time that, during the tracing phase of garbage collection, all Rust objects visible to the GC
will report all contained pointers to other GC values, avoiding the threat of incorrectly collecting reachable values.
Furthermore, we restrict the ways our wrappers around SpiderMonkey pointers can be manipulated, thus turning
potential runtime memory leaks and ownership semantic API mismatches into static compiler errors instead.

Future plans include refining our safety checks for garbage collected values, such as flagging invalid ownership
transference, and introducing compile-time checks for constructs that are non-optimal in terms of performance or
memory usage.
